\chapter*{Abstract}

Accidents is the 4th leading cause of death for all ages in the Philippines. One of the top five leading causes of death due to accidents in the Philippines for all ages is accidental falls.  From worldwide statistics, 138 children, aged 0 to 18 years die daily due to falls. This translates to around 50,000 children dying each year due to accidental falls. It counts as the
fifth leading cause of unintentional deaths of children below 14 years old in the Philippines.
Falls were also found to be the leading cause of morbidity and lifelong disability among
children. \cite{Cri14}

The goal of this project is to design and develop a device that can detect motion of user such as standing, sitting, lying, walking and falling with direction detection of fall whether the fall is in forward, sideward or backward motion. This project produced the said device and was successfully developed with 95\% of the devices accuracy of detection. When falling motion was established, the notification system of the device was activated, and message was sent to the recorded responder/s with details such as location of fall, time of fall, name of user who has fallen and the date of fall.

The use of two accelerometers located at the hip and thigh resulted as a good component
in making a motion detection device with 92.22\% reliability. The development of falling
device that can recognize direction of fall with the use of the same two modules resulted
with 92.22\% of accuracy. Motion detection such as standing, sitting, walking and lying that are sub-feature of this device was successfully detected with 97.5\% overall accuracy rate. In general view of the device’s performance, the design and development of fall analyzer with specific motion detection which can be personalized with the function of send notification message to recorded responder/s during the fall was achieved with above 80\% acceptable accuracy rate.


